\documentclass[conference]{IEEEtran}

\pagestyle{headings}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{color}
\usepackage{tabularx}
\usepackage{todonotes}
\usepackage{tabto}
\usepackage{url}
\usepackage{csquotes}
\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,matrix,fit,backgrounds,calc}

\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\newcommand{\assign}{\ensuremath{\leftarrow }}

\newcommand{\underapp}[1]{\ensuremath{#1^\downarrow}}
\newcommand{\overapp}[1]{\ensuremath{#1^\uparrow}}

\newcommand{\True}{\ensuremath{\top}}
\newcommand{\False}{\ensuremath{\bot}}
\newcommand{\Undef}{\ensuremath{\mathbf{U}}}
\newcommand{\SAT}{\ensuremath{\mathsf{SAT}}}
\newcommand{\UNSAT}{\ensuremath{\mathsf{UNSAT}}}
\newcommand{\UNDEF}{\ensuremath{\mathsf{UNDEF}}}

\newcommand{\Vars}[1]{\mathsf{vars}(#1)}
\newcommand{\Lits}[1]{\mathsf{lits}(#1)}
\newcommand{\Enc}[1]{\mathsf{enc}(#1)}

\makeatletter
\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
\makeatother

\title{System Description of Candy Kingdom --\\ A Sweet Family of SAT Solvers}
\author{Markus Iser, Felix Kutzner}
% TODO: add institute etc
%\institute{
%  Karlsruhe Institute of Technology (KIT), Germany\\
%  \url{{markus.iser, felix.kutzner}@kit.edu}
%}

\begin{document}

\maketitle

\begin{abstract}
Candy is a branch of the Glucose 3 SAT solver and started as a refactoring effort towards modern C++.
We replaced most of its custom lowest-level data structures and algorithms by their C++ standard library equivalents and improved or reimplemented several of its components.
New functionality in Candy is based on gate structure analysis and random simulation. 
\end{abstract}

\section{Introduction}

The development of our open-source SAT solver \textbf{Candy}\footnote{\url{https://github.com/udopia/candy-kingdom}} started as a branch of the well-known \textbf{Glucose} \cite{Audemard:2009:Glucose} CDCL SAT solver (version 3.0).
With Candy, we aim to facilitate the solver's development by refactoring the Glucose source code towards modern C++ and by reducing dependencies within the source code.
This involved replacing most custom lowest-level data structures and algorithms by their C++ standard library equivalents.
The refactoring effort enabled high-level optimizations of the solver such as inprocessing and cache-efficient clause memory management.
We also increased the extensibility of Candy via static polymorphism, e.g. allowing the solver's decision heuristic to be customized without incurring the overhead of dynamic polymorphism. This enabled us to efficiently implement variants of the Candy solver.
Furthermore, we modularized the source code of Candy to make its subsystems reusable.
The quality of Candy is assured by automated testing, with the functionality of Candy tested on different compilers (clang, gcc, Microsoft C/C++) and operating systems (Linux, Apple macOS, Microsoft Windows) using continuous integration systems.
In what follows, we present the optimizations we implemented in Candy and describe two variants of the solver.

\section{Clause Memory Management}
\label{sec:clauses}

In contrast to Glucose, in Candy clauses are now referenced as regular pointers and for fast access and optimized cache usage we introduced a dedicated memory management. Clauses are optimized for size so we have a very small clause header that keeps size, activity, lbd value and only a few flags. Our clause allocator preallocates clauses in buckets of equivalently sized clauses up to clauses of length $500$. Only clauses exceeding that size limit are allocated by regular new/delete methods. Memory for small clauses is regularly revamped such that the clauses are sorted by their activity (in memory) with the highest activity first. Also the watchers are sorted by clause size and activity. 

\section{Improved Incremental Mode}

We made several clause simplifications work in incremental mode that have been deactivated before in Glucose. Also a certificate can be generated in incremental mode if assumptions are used properly. In incremental mode for certificate generation Candy suppresses output of learnt clauses containing assumptions as well as the output of the empty clause as long as assumptions are used in the final conflict. 

\section{Inprocessing}

We improved the architecture of clause simplification such that Candy can now perform subsumption and self-subsuming resolution during search. Clauses of the original problem are included as well as learnt clauses that are persitent in the learnt clause database (that includes clauses of size 2 and clauses with lbd <= 2). 

\section{Gate Structure Analysis and Applications}

Candy provides modules for gate extraction \cite{Iser:2015:GateRecognition} and random simulation \cite{krohm1996use}.
Detemerminized random simulation is used on gate structure extracted from SAT problems to generate conjectures about literal equivalences and backbone variables.
The Candy solver variant Candy/RSAR uses these conjectures to compute and iteratively refine under-approximations of the SAT problem instance \cite{Kutzer:2016:Thesis}.
The Candy solver variant Candy/RSIL uses branching heuristics based on implicit learning \cite{Kutzer:2016:Thesis,DBLP:journals/jucs/LuWCMH04} to stimulate clause learning by violating extracted conjectures about variable equivalencies where possible, otherwise using the VSIDS branching heuristic.
Candy/RSIL includes the sub-variants Candy/RSILv, with which the probability of implicit learning being used is successively halved after a fixed amount of decisions, and Candy/RSILi, with which usage budgets are assigned to each of the two implications represented by a conjecture.
If budgets are assigned, such an implication can be used for implicit learning only if its budget is nonzero, and an implication's budget is decreased every time it is used for implicit learning.

Employing implicit learning has proven particularly efficient for solving miter problems with general-purpose SAT solvers \cite{Kutzer:2016:Thesis}.
Candy includes fast miter problem detection heuristics enabling implicit learning to be enabled only for SAT problem instances detected to be miter encodings within a given time limit.
For a general description of miter problems, see e.g. \cite{hwmcc12Bench}.

\bibliographystyle{splncs03}
%\bibliographystyle{abbrv}
\bibliography{abstractionrefinement,blockedsets,general,preprocessing,structurerecognition,applications,encodings,otherstructure,self}

\end{document}
